---
title: "Cabbages"
author: "Davy Dargan"
date: "31.1.2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction


<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following question.  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
predict VitC based on cultivation method.
VitC is numerical
Cultivation is catergorical, so use the numerical-cat helper file.


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
plot(VitC~Cult,data=veggy)
```


This graph shows the cultivation method c52 produces more VitC in cabbage.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results
```{r}
favstats(VitC~Cult,data=veggy)
```

The mean number of VitC in cultivation method c52 shows a higher average VitC level than that of that cultivation method c39.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results
```{r}
t.test(VitC~Cult,data=veggy)
```

the p-value is 0.00000003405 < 0.05 you reject the null hypothesis and the cultivation method c52 produces more VitC than cultivation method c39.

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion
the original question asks is there a difference in VitC in cultivation methods of cabbage. We reject the null hypothesis that there is no difference in cultivation methods and VitC with a p-value of less than 0.05 We can conclude that method c52 produces more VitC in cabbage than c39.


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
